\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\input{glyphtounicode}

\pagestyle{fancy}\fancyhf{}\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.35in}

\urlstyle{same}
\raggedbottom\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\bfseries\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1\vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-9pt}}
\newcommand{\resumeSubSubheading}[2]{
  \item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

\begin{document}

\begin{center}
  {\LARGE \textbf{Siyu (Zoey) Ai}} \\[3pt]
  \small
  (206) 581-6158 $\mid$
  \href{mailto:Zoey.Ai@outlook.com}{Zoey.Ai@outlook.com} $\mid$
  Seattle, WA $\mid$
  \href{https://www.linkedin.com/in/zoeyai/}{linkedin.com/in/zoeyai/} $\mid$
  \href{https://github.com/zoeyai1221}{GitHub}
\end{center}

\section{Summary}
\resumeSubHeadingListStart
  \item\small{Finance and Operations professional with 5+ years of experience building financial planning infrastructure and operational systems from the ground up across high-growth tech environments. Proven track record owning end-to-end FP\&A, budgeting, and cross-functional program management in both large-scale organizations and early-stage startup settings. MS in Computer Science adds technical depth to financial modeling and data-driven decision-making.
}
\resumeSubHeadingListEnd

\vspace{-15pt}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading{Northeastern University}{Seattle, Washington}{Master of Science in Computer Science, \textbf{ GPA: }4.0/4.0}{September 2023 -- \textbf{April 2026}}
  \resumeSubheading{The University of Texas at Dallas}{Dallas, Texas}{Master of Science in Finance \& Business Analytics, GPA: 3.65/4.0}{August 2016 -- May 2019}
  \resumeSubSubheading{Honors: Dean's Excellent Scholarship, Dean's Impact Scholarship, Certified Excellent Graduate Student}{}
  \vspace{0pt}
  \resumeSubheading{Shenyang University of Technology}{Shenyang, China}{Bachelor of Science in Finance}{September 2011 -- June 2015}
\resumeSubHeadingListEnd

\vspace{-6pt}

\section{Work \& Leadership Experience}
\resumeSubHeadingListStart
  \resumeSubheading{Amazon Web Services, Inc.}{Shanghai, China}{Business Operations Manager, Central Strategy Planning Team}{February 2022 -- August 2023}
  \resumeItemListStart
    \resumeItem{Drove end-to-end design and implementation of business operations programs and tools for AWS China, directly supporting organizational goals and delivering measurable productivity gains across 1,000+ field sales reps and operations teams.}
    \resumeItem{Owned the weekly business reporting product for GCR leadership; authored a 100+ page report synthesizing key sales performance metrics, establishing it as the primary visibility tool for executive decision-making.}
    \resumeItem{Designed and led end-to-end delivery of AWS China's Anaplan-based sales forecasting platform, coordinating requirements across 20+ cross-functional teams and scaling adoption to 1,000+ field reps across multiple sales BUs and territories.}
    \resumeItem{Orchestrated strategic alignment between GCR C-suite and 20+ sales, technical, and functional teams; translated executive priorities into operational roadmaps and coordinated delivery across a \$3.5B+ annual revenue business spanning diverse partner and customer segments.}
    \resumeItem{Built SQL and Tableau analytics pipelines processing 600K+ monthly sales records across 60+ BUs/sub-BUs; surfaced performance insights driving data-based strategic decisions and reducing manual reporting effort by 90\% across the organization.}
  \resumeItemListEnd

  \resumeSubheading{Amazon.com, Inc.}{Seattle, Washington}{Financial Analyst, Amazon Logistics Team}{May 2020 -- February 2022}
  \resumeItemListStart
    \resumeItem{Built from the ground up the full financial planning infrastructure for a newly established division; designing monthly, quarterly, and annual budgeting, forecasting, and a three-year strategic plan across 20+ business units and 300+ delivery stations with \$400M+ annual budget. }
    \resumeItem{Served as financial and operational lead across product, engineering, construction, and real estate teams to drive the launch and rapid scaling of Amazon Logistics’ One-Day Delivery initiative, aligning CAPEX deployment with operational milestones. }
    \resumeItem{Identified and closed data visibility gap across NA logistics network by independently scoping and delivering a centralized tracking system across 300+ stations, enabling consistent cross-team reporting and planning.}
    \resumeItem{Built automated financial forecasting models using Python (Pandas, NumPy) and SQL on historical cost data to detect cost patterns and seasonality, improving forecast accuracy by 30\% and reducing manual analysis cycles.}
  \resumeItemListEnd

  \resumeSubheading{Huawei Technologies, Inc.}{Plano, Texas}{Financial Planning Analyst, Finance Department}{September 2018 -- February 2020}
  \resumeItemListStart
    \resumeItem{Provided financial analysis and control of 40+ R\&D projects with a total budget of over \$60M for annual budgeting; analyzed key financial performance indicators and performed variance analysis of actual vs.\ budget and forecast.}
    \resumeItem{Developed monthly rolling forecast based on normalized historical cost analysis and direct input from business and tracked forecast accuracy; achieved overall spend execution rate of 94\%, highly aligned with strategic objectives.}
    \resumeItem{Defined business requirements, logical data and process design for operational and financial systems; provided regular training to over 50 executive assistants on Workday ERP and financial query tools.}
    \resumeItem{Consolidated and processed 500K+ monthly expense records from 30+ enterprise systems (MS Access, SQL Server, Oracle ERP), ensuring data integrity and delivering monthly financial reports for executive and Fortune 500 parent company review.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\resumeSubHeadingListStart
  \item\small{\begin{tabular*}{0.97\textwidth}{p{0.97\textwidth}}
      \textbf{Advanced Excel Analytics}: {PivotTables, VLOOKUP, Index, Data Validation, What-If Analysis, Solver, Macro, VBA.} \\
      \textbf{Platform / Tools}: {MySQL, MS Access, Oracle ERP, Workday, Salesforce, Tableau, QuickSight, Power BI, Redshift, Cognos.} \\
      \textbf{Programming Languages}: {SQL, Python, R, SAS, Java, TypeScript.} \\
  \end{tabular*}}
\resumeSubHeadingListEnd

\end{document}
