\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\input{glyphtounicode}

\pagestyle{fancy}\fancyhf{}\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.35in}

\urlstyle{same}
\raggedbottom\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\bfseries\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1\vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-9pt}}
\newcommand{\resumeSubSubheading}[2]{
  \item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{
  \item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

\begin{document}

\begin{center}
  {\LARGE \textbf{Siyu (Zoey) Ai}} \\[3pt]
  \small
  (206) 581-6158 $\mid$
  \href{mailto:Zoey.Ai@outlook.com}{Zoey.Ai@outlook.com} $\mid$
  Seattle, WA $\mid$
  \href{https://www.linkedin.com/in/zoeyai/}{linkedin.com/in/zoeyai/} $\mid$
  \href{https://github.com/zoeyai1221}{GitHub}
\end{center}

\section{Summary}
\resumeSubHeadingListStart
  \item\small{Technology and operations professional with 5+ years delivering enterprise SaaS tools, internal platforms, and consumer applications at Amazon, AWS, and early-stage startups. Experienced across the full product lifecycle, from requirements definition, Agile development, and UAT to cross-functional adoption, with dual Finance and CS backgrounds enabling fluent partnership across business, data, and engineering teams.
}
\resumeSubHeadingListEnd

\vspace{-10pt}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading{Northeastern University}{Seattle, Washington}{Master of Science in Computer Science, \textbf{ GPA:} 4.0/4.0}{September 2023 -- \textbf{April 2026}}
  \resumeSubheading{The University of Texas at Dallas}{Dallas, Texas}{Master of Science in Finance \& Business Analytics, GPA: 3.65/4.0}{August 2016 -- May 2019}
  \resumeSubSubheading{Honors: Dean's Excellent Scholarship, Dean's Impact Scholarship, Certified Excellent Graduate Student}{}
\resumeSubHeadingListEnd

\section{Technical Skills}
\resumeSubHeadingListStart
  \item\small{\begin{tabular*}{0.97\textwidth}{p{0.97\textwidth}}
      \textbf{Product Management}: {Agile/Scrum, Figma, User Story Prioritization, Roadmap Planning, OKR, Jira, GitHub Projects.} \\
      \textbf{Data Analytics \& Databases}: {Tableau, QuickSight, Power BI, SQL, Excel Analytics; MySQL, SQL Server, MongoDB.} \\
      \textbf{Programming}: {Python, Java, JavaScript, TypeScript, HTML, CSS, R, SAS.} \\
  \end{tabular*}}
\resumeSubHeadingListEnd

\vspace{-12pt}

\section{Work \& Leadership Experience}
\resumeSubHeadingListStart
  \resumeSubheading{SlicPix, Inc.}{Seattle, Washington}{Software Engineer Co-op, Technology Department}{September 2025 -- January 2026}
  \resumeItemListStart
    \resumeItem{Owned end-to-end delivery of Shopify app extension, defining scope from user requirements through UAT and launch; successfully onboarded 20+ Braveheart users with positive adoption feedback.}
    \resumeItem{Partnered with founder to evaluate GTM strategy and investor pitch framing, translating technical product capabilities into business value narratives for external stakeholders.}
  \resumeItemListEnd

  \resumeSubheading{Amazon Web Services, Inc.}{Shanghai, China}{Business Operations Manager, Central Strategy Planning Team}{February 2022 -- August 2023}
  \resumeItemListStart
    \resumeItem{Led end-to-end product delivery of an automated sales forecasting tool: gathered requirements from 20+ teams, designed UI layout, authored UAT scripts across 4 user personas, and ran GCR leadership roadshow to drive adoption across 700+ territories and 1,000+ field reps.}
    \resumeItem{Owned the weekly business reporting product for GCR leadership: designed a 3-phase rollout across 14 sales and function teams and synthesized requirements from 50+ stakeholders, reducing per-team manual reporting effort by 90\%.}
    \resumeItem{Acted as strategic liaison between C-suite and cross-functional teams, translating executive priorities into actionable roadmaps and aligning 20+ sales, technical, and operations teams around shared delivery milestones.}
    \resumeItem{Analyzed 600K+ monthly sales records using SQL and Tableau to surface product performance insights, directly informing sales strategy and operational decisions for AWS China (\$3.5B+ annual revenue).}
  \resumeItemListEnd

  \resumeSubheading{Amazon.com, Inc.}{Seattle, Washington}{Financial Analyst, Amazon Logistics Team}{May 2020 -- February 2022}
  \resumeItemListStart
    \resumeItem{Identified gap in financial data visibility across the NA logistics network and independently scoped, built, and drove adoption of a centralized tracking system across 300+ stations, reducing data discrepancies and improving planning reliability.}
    \resumeItem{Partnered with product, engineering, and real estate teams to align \$400M+ annual CAPEX planning with station launch roadmaps, serving as the financial decision-making partner for cross-functional execution.}
    \resumeItem{Identified an untracked capital spend category and led stakeholder alignment sessions with PM team leads to define data requirements and template structure, establishing the first systematic budgeting process for ad-hoc special projects across the NA logistics network.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading{\textbf{PalUp} \emph{(Social Activity Matching Web Application)}}{}
  \resumeItemListStart
    \resumeItem{Conceptualized and led product discovery for PalUp, a community-driven platform connecting locals and travelers; conducted deep-dive user interviews to define core use cases and translated insights into a prioritized backlog of 20+ user stories, balancing user experience with engineering constraints.}
    \resumeItem{Orchestrated Agile development cycles, directing cross-functional teams through 4 bi-weekly sprints; proactively managed the product roadmap and resolved technical blockers to achieve a 95\% milestone completion rate.}
    \resumeItem{Designed end-to-end product experience in Figma from sketches to high-fidelity prototype; conducted user testing and heuristic evaluations across core task flows, identifying and resolving 10+ usability issues --- recognized by professor as a course Hall of Fame prototype.}
  \resumeItemListEnd

  \resumeProjectHeading{\textbf{Study Buddy Find Chatbot} \emph{(Discord, Agile/Scrum)}}{}
  \resumeItemListStart
    \resumeItem{Designed and launched a Discord chatbot to enhance peer-to-peer study collaboration for 300+ students, integrating user preferences to provide personalized peer matching and driving engagement through tailored interactions.}
    \resumeItem{Conducted in-depth user research and requirement analysis, translating student needs into 20+ detailed user stories with clear acceptance criteria to ensure user-focused outcomes and technical feasibility.}
    \resumeItem{Managed Agile development cycles, leading four 2-week sprints and achieving a 95\% milestone completion rate while tracking and resolving 100+ issues through GitHub Projects to ensure on-time delivery.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
