\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\input{glyphtounicode}

\pagestyle{fancy}\fancyhf{}\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.35in}

\urlstyle{same}
\raggedbottom\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\bfseries\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1\vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-9pt}}
\newcommand{\resumeProjectHeading}[2]{
  \item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{
  \item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

\begin{document}

\begin{center}
  {\LARGE \textbf{Siyu (Zoey) Ai}} \\[3pt]
  \small
  (206) 581-6158 $\mid$
  \href{mailto:Zoey.Ai@outlook.com}{Zoey.Ai@outlook.com} $\mid$
  Seattle, WA $\mid$
  \href{https://www.linkedin.com/in/zoeyai/}{linkedin.com/in/zoeyai/} $\mid$
  \href{https://github.com/zoeyai1221}{GitHub}
\end{center}

\section{Technical Skills}
\resumeSubHeadingListStart
  \item\small{\begin{tabular*}{0.97\textwidth}{p{0.97\textwidth}}
      \textbf{Enterprise Systems \& Frameworks}: {Oracle ERP, Workday, Salesforce, ERP System Implementation, UAT, SDLC.} \\
      \textbf{Data \& Analytics}: {Advanced Excel, SQL, Python, Tableau, QuickSight, ETL Pipelines, Data Modeling, Data Visualization.} \\
      \textbf{Business Operations}: {Strategic Financial Planning, Forecast \& Variance Analysis, GTM Strategy Review, Process Automation.} \\
  \end{tabular*}}
\resumeSubHeadingListEnd

\vspace{-12pt}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading{Northeastern University}{Seattle, Washington}{Master of Science in Computer Science, \textbf{ GPA:} 4.0/4.0}{September 2023 -- \textbf{April 2026}}
  \resumeSubheading{The University of Texas at Dallas}{Dallas, Texas}{Master of Science in Finance \& Business Analytics, GPA: 3.65/4.0}{August 2016 -- May 2019}
  \resumeSubSubheading{Honors: Dean's Excellent Scholarship, Dean's Impact Scholarship, Certified Excellent Graduate Student}{}
\resumeSubHeadingListEnd

\section{Work \& Leadership Experience}
\resumeSubHeadingListStart
  \resumeSubheading{SlicPix, Inc.}{Seattle, Washington}{Software Engineer Co-op, Technology Department}{September 2025 -- January 2026}
  \resumeItemListStart
    \resumeItem{Led UAT process for AI-powered features across Shopify app extension and Interactive Studio 2.0, validating backend-frontend interactions against business requirements and documenting system behavior for maintainable handover.}
    \resumeItem{Partnered with founding team on product scoping and release readiness, aligning cross-functional technical and operational requirements with go-to-market timelines to support user acquisition.}
    \resumeItem{Supported GTM strategy and investor pitch framing, translating technical capabilities into business value narratives.}
  \resumeItemListEnd

  \resumeSubheading{Amazon Web Services, Inc.}{Shanghai, China}{Business Operations Manager, Central Strategy Planning Team}{February 2022 -- August 2023}
  \resumeItemListStart
    \resumeItem{Orchestrated strategic alignment between GCR C-suite and 20+ sales, technical, and functional teams; translated executive priorities into operational roadmaps and coordinated delivery across a \$3.5B+ annual revenue business.}
    \resumeItem{Defined requirements and led end-to-end delivery of an Anaplan-based automated sales forecasting tool, mapping local business structure and hierarchy into system logic; improved forecasting efficiency for 1,000+ field sales reps.}
    \resumeItem{Designed and owned a 100+ page weekly business reporting system, consolidating inputs from 50+ stakeholders into a standardized executive reporting framework that became the single source of truth for GCR leadership.}
    \resumeItem{Built SQL and Tableau pipelines to process 600K+ monthly sales records into structured dashboards, enabling data-driven operational decisions and reducing manual reporting effort by 90\%.}
    \resumeItem{Delivered weekly competitive benchmarking and product performance analyses to GCR C-suite and 6 sales BUs; translated data insights into GTM recommendations that directly informed AWS China's annual sales planning.}
    \resumeItem{Automated monthly revenue collection across 60+ BUs/sub-BUs using Python and Excel; reverse-engineered backend field requirements to design a single pipeline serving both executive dashboards and system ingestion.}
  \resumeItemListEnd

  \resumeSubheading{Amazon.com, Inc.}{Seattle, Washington}{Financial Analyst, Amazon Logistics Team}{May 2020 -- February 2022}
  \resumeItemListStart
    \resumeItem{Identified and closed data visibility gap across NA logistics network by independently scoping and delivering a centralized tracking system across 300+ stations, enabling consistent cross-team reporting and planning.}
    \resumeItem{Partnered with product, engineering, and real estate teams as financial decision-making lead for 300+ station launches; aligned cross-functional execution with \$400M+ annual CAPEX strategy.}
    \resumeItem{Developed automated forecasting models using Python and SQL to detect cost patterns and seasonality across historical data, improving forecast accuracy by 30\% and reducing manual analysis cycles.}
    \resumeItem{Championed ERP and BI tool adoption across finance and operations teams; designed training materials, maintained system documentation, and standardized reporting workflows to ensure data integrity across 300+ logistics stations.}
  \resumeItemListEnd

  \resumeSubheading{Huawei Technologies, Inc.}{Plano, Texas}{Financial Planning Analyst, Finance Department}{September 2018 -- February 2020}
  \resumeItemListStart
    \resumeItem{Administered Workday ERP rollout for 50+ Finance and executive end users; designed onboarding workflows, standardized data entry processes, and resolved configuration issues to ensure system adoption and improve planning efficiency by 50\%.}
    \resumeItem{Consolidated and processed 500K+ monthly expense records from 30+ enterprise systems (MS Access, SQL Server), ensuring data integrity and delivering monthly financial reports for executive review.}
    \resumeItem{Managed forecasting and budgeting processes for 40+ R\&D projects (\$60M+ budget); tracked forecast accuracy and variance against actuals, achieving 94\% spend execution rate.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Project}
\resumeSubHeadingListStart
  \resumeProjectHeading{\textbf{Database System Design \& Business Logic Modeling} \emph{(MySQL, Java, DAO Pattern)}}{}
  \resumeItemListStart
    \resumeItem{Designed a relational database (MySQL) modeling 20+ business entities; applied BCNF normalization and referential integrity constraints to translate stakeholder requirements into a governed, scalable data architecture.}
    \resumeItem{Translated complex business rules into a Java-based backend using the DAO pattern, mapping domain logic to system behavior; documented data flows and functional specifications to bridge business requirements with technical implementation.}
    \resumeItem{Built a web-based analytics dashboard for real-time multi-dimensional reporting; defined functional requirements for security controls (SQL injection prevention) and validated system reliability against acceptance criteria.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
