\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\input{glyphtounicode}

\pagestyle{fancy}\fancyhf{}\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.35in}

\urlstyle{same}
\raggedbottom\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\bfseries\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1\vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-9pt}}
\newcommand{\resumeSubSubheading}[2]{
  \item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{
  \item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-6pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

\begin{document}

\begin{center}
  {\LARGE \textbf{Siyu (Zoey) Ai}} \\[3pt]
  \small
  (206) 581-6158 $\mid$
  \href{mailto:Zoey.Ai@outlook.com}{Zoey.Ai@outlook.com} $\mid$
  Seattle, WA $\mid$
  \href{https://www.linkedin.com/in/zoeyai/}{linkedin.com/in/zoeyai/} $\mid$
  \href{https://github.com/zoeyai1221}{GitHub}
\end{center}

\section{Summary}
\resumeSubHeadingListStart
  \item\small{Operations and strategy professional with experience driving cross-functional execution and building data-driven decision infrastructure. Proven track record translating executive priorities into operational programs, surfacing business insights from large-scale data, and delivering measurable results in both large-scale global enterprises and early-stage environments. MS in Computer Science adds technical depth for analytics and systems-level thinking.}
\resumeSubHeadingListEnd

\vspace{-6pt}
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading{Northeastern University}{Seattle, Washington}{Master of Science in Computer Science, \textbf{ GPA: }4.0/4.0}{September 2023 -- \textbf{April 2026}}
  \resumeSubheading{The University of Texas at Dallas}{Dallas, Texas}{Master of Science in Finance \& Business Analytics, GPA: 3.65/4.0}{August 2016 -- May 2019}
  \resumeSubSubheading{Honors: Dean's Excellent Scholarship, Dean's Impact Scholarship, Certified Excellent Graduate Student}{}
\resumeSubHeadingListEnd

\section{Work \& Leadership Experience}
\resumeSubHeadingListStart
  \resumeSubheading{SlicPix, Inc.}{Seattle, Washington}{Software Engineer Co-op, Technology Department}{September 2025 -- January 2026}
  \resumeItemListStart
    \resumeItem{Partnered with founding team to align operational and technical priorities with business objectives; contributed to go-to-market planning and cross-functional execution in a 0-to-1 startup environment.}
    \resumeItem{Translated product capabilities into strategic positioning and financial narratives for investor and leadership communications, supporting early-stage business development.}
  \resumeItemListEnd

  \resumeSubheading{Amazon Web Services, Inc.}{Shanghai, China}{Business Operations Manager, Central Strategy Planning Team}{February 2022 -- August 2023}
  \resumeItemListStart
    \resumeItem{Orchestrated strategic alignment between GCR C-suite and 20+ sales, technical, and functional teams; translated executive priorities into operational roadmaps across a \$3.5B+ annual revenue business.}
    \resumeItem{Owned the weekly business reporting product for GCR leadership, consolidating inputs from 50+ stakeholders into a 100+ page executive reporting framework that became the primary visibility tool for organizational decision-making.}
    \resumeItem{Designed and delivered AWS China's Anaplan-based sales forecasting platform end-to-end, coordinating requirements across 20+ cross-functional teams and scaling adoption to 1,000+ field reps.}
    \resumeItem{Built SQL and Tableau analytics pipelines processing 600K+ monthly sales records; surfaced performance insights reducing manual reporting effort by 90\% and enabling data-driven operational decisions across the organization.}
    \resumeItem{Delivered weekly competitive benchmarking and market performance analyses to GCR C-suite and 60+ BUs/sub-BUs; translated insights into GTM recommendations that directly informed AWS China's annual sales planning.}
  \resumeItemListEnd

  \resumeSubheading{Amazon.com, Inc.}{Seattle, Washington}{Financial Analyst, Amazon Logistics Team}{May 2020 -- February 2022}
  \resumeItemListStart
    \resumeItem{Served as cross-functional execution lead across product, engineering, construction, and real estate teams to drive the launch and rapid scaling of Amazon Logistics' One-Day Delivery initiative, aligning \$400M+ annual CAPEX deployment with operational milestones.}
    \resumeItem{Identified and closed data visibility gap across the NA logistics network by independently scoping and delivering a centralized tracking system across 300+ stations, enabling consistent cross-team reporting and planning.}
    \resumeItem{Built automated forecasting models using Python (Pandas, NumPy) and SQL to detect cost patterns and seasonality, improving forecast accuracy by 30\% and enabling proactive resource planning.}
  \resumeItemListEnd

  \resumeSubheading{Huawei Technologies, Inc.}{Plano, Texas}{Financial Planning Analyst, Finance Department}{September 2018 -- February 2020}
  \resumeItemListStart
    \resumeItem{Managed planning and operations for 40+ R\&D projects (\$60M+ budget); tracked forecast accuracy and variance against actuals, achieving a 94\% spend execution rate aligned with strategic objectives.}
    \resumeItem{Led end-to-end process design and system rollout for financial operations across 50+ executive stakeholders; standardized data workflows and improved planning efficiency by 50\%.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\resumeSubHeadingListStart
  \item\small{\begin{tabular*}{0.97\textwidth}{p{0.97\textwidth}}
      \textbf{Strategic Operations}: {Cross-functional Program Management, Business Strategy, Executive Reporting, OKR/KPI Frameworks, Go-to-Market Execution, Process Design \& Automation.} \\
      \textbf{Data \& Analytics}: {SQL, Python (Pandas, NumPy), Tableau, Power BI, QuickSight, Advanced Excel (VBA, PivotTables).} \\
      \textbf{Tools}: {Anaplan, Oracle ERP, Workday, Salesforce.} \\
  \end{tabular*}}
\resumeSubHeadingListEnd

\vspace{-6pt}

\section{Research Project}
\resumeSubHeadingListStart
  \resumeProjectHeading{\textbf{AI-Powered Clinical Assessment Automation} \emph{(Graduate Research)}}{January 2026 -- April 2026}
  \resumeItemListStart
    \resumeItem{Designed a structured feasibility study evaluating 7 AI models across 43 experimental configurations to automate clinical pet health assessment --- a diagnostic task previously dependent on per-case expert veterinary judgment.}
    \resumeItem{Demonstrated a fine-tuned open-source model outperformed Google Gemini 3.1 Pro (mean deviation: 0.94 vs.\ 0.98) at a fraction of deployment cost, producing a clear build-vs-buy recommendation for AI product adoption.}
    \resumeItem{Quantified that prompt design strategy alone drove up to 40\% accuracy improvement without additional training cost, establishing a reusable framework for AI system optimization across cost and performance constraints.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
